This page and the next page should be removed

### 2021-01-17 analysis/manuscript.Rmd
update grand averaging with dict comprehension

```{r setup, include=FALSE}
# Load packages
library(papaja)
library(reticulate)
library(tidyverse)
library(magrittr)
library(cowplot)

@@

# Do you want to re-run the EEG preprocessing? Note that this can only be used with the raw EEG data, which are
# available from the corresponding author (rasha.abdel.rahman@hu-berlin.de) upon request.
rerun_preproc <- FALSE

# Do you want to re-run the linear mixed-effect models? This can be done even if only the preprocessed single-trial
# data are available (from GitHub and/or the OSF). Note, however, that the model fitting may take more than 24 hours.
rerun_models <- FALSE
```

@@

```{r exp1-preparation, eval=rerun_preproc}
# Define function for reading and formatting the behavioral data
read_behav <- function(txt_fname) {
  # Read the log file
  dat <- suppressWarnings(read_tsv(txt_fname, col_types = cols()))
  # Rename columns for participant and item IDs
  dat %<>% rename(participant = VPNummer, item = StimID) %>%
    # Add a column for the part of the experiment
    mutate(part = case_when(
      Wdh %in% c(211, 231) ~ "I",
      Wdh %in% c(212, 232) ~ "II",
      Wdh %in% c(213, 233) ~ "III",
      Wdh == 234 ~ "IV"
    ) %>% as_factor()) %>%
    # Remove filler stimuli (i.e.,well-known objects)
    filter(bek_unbek != "bekannt")
  # Assign stimuli to conditions based on keywords and button presses
  excl_known <- dat %>% filter(part == "I" & Tastencode %in% c(201, 251)) %>% pull(item)
  excl_informed <- dat %>% filter(part == "II" & grepl("richtig", Bed) & !Tastencode %in% c(201, 202, 251, 252)) %>% pull(item)
  excl_naive <- dat %>% filter(part == "II" & grepl("falsch", Bed) & !Tastencode %in% c(203, 204, 253, 254)) %>% pull(item)
  informed <- dat %>% filter(part == "II" & grepl("richtig", Bed) & Tastencode %in% c(201, 202, 251, 252)) %>% pull(item)
  naive <- dat %>% filter(part == "II" & grepl("falsch", Bed) & Tastencode %in% c(203, 204, 253, 254)) %>% pull(item)
  # Create a new condition for the experimental condition
  dat %<>% mutate(condition = case_when(
    item %in% excl_known ~ "Excl_known",
    item %in% excl_informed ~ "Excl_informed",
    item %in% excl_naive ~ "Excl_naive",
    item %in% informed ~ "Informed",
    item %in% naive ~ "Naive"
  ) %>% factor(levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")))
  # In Experiment 3, we need an additional column for position (upright vs. inverted)
  if ("richtig_inv" %in% dat$Bed) {
    dat %<>% mutate(position = as_factor(ifelse(grepl("inv", Bed), "Inverted", "Upright"))) %>%
      # Return only relevant columns
      select(part, position, condition, participant, item, RT)
  } else {
    # Return only relevant columns
    dat %<>% select(part, condition, participant, item, RT)
  }
  return(dat)
}

# Read behavioral data for Experiment 1
data_exp1 <- list.files("data/exp1/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav)

# Check average number of stimuli per condition and save to the export folder
map(data_exp1, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  colMeans() %>%
  saveRDS("analysis/export/exp1-stims.RDS")
```

```{python exp1-preprocessing, eval=rerun_preproc}
# Import libraries
import mne
import glob
import os

# Set parameters for EEG preprocessing
preproc_params = dict(
    n_components=15, method='fastica',         # ICA parameters
    l_freq=0.1, h_freq=30,                     # Filter edges
    event_id={'match': 221, 'mismatch': 222},  # EEG triggers
    tmin=-0.5, tmax=1.498,                     # Length of epochs
    baseline=(-0.2, 0),                        # Baseline correction
    reject=dict(eeg=200)                       # Rejection threshold
)

# # For debugging
# locals().update(preproc_params)
# vhdr_fname = 'data/exp1/EEG/Vp0001.vhdr'

@@

# List raw EEG filenames
fnames_exp1 = sorted(glob.glob('data/exp1/EEG/*.vhdr'))

# Import behavioral data from R
metadata_exp1 = r.data_exp1

# Apply the function to preprocess the EEG data for Experiment 1
epochs_exp1 = [preproc(vhdr_fname=fname, metadata=meta, **preproc_params)
               for fname, meta in zip(fnames_exp1, metadata_exp1)]

# Combine epochs into a single data set
epochs_exp1 = mne.concatenate_epochs(epochs_exp1)

# Backup epochs to the export folder
epochs_exp1.save('analysis/export/exp1-epo.fif')

# Backup the channel names separately

# Check if preprocessing was done already (delete the file to re-run)
if os.path.exists('analysis/export/exp1-epo.fif'):
    # Read preprocessed data from file
    epochs_exp1 = mne.read_epochs('analysis/export/exp1-epo.fif', preload=True)
else:
    # Preprocess EEG data for Experiment 1
    epochs_exp1 = [preproc(vhdr_fname=fname, metadata=meta, **preproc_params)
                   for fname, meta in zip(fnames_exp1, metadata_exp1)]
    # Combine epochs into a single data set
    epochs_exp1 = mne.concatenate_epochs(epochs_exp1)
    # Backup epochs to the export folder
    epochs_exp1.save('analysis/export/exp1-epo.fif')

# Define function to compute grand averages per condition
def compute_evokeds(epochs):
    evokeds = dict(); evokeds_dat = dict()
    # Each part becomes a dictionary of conditions
    for pt in ['I', 'II', 'III']:
        evokeds[pt] = dict(); evokeds_dat[pt] = dict()
        # Each condition becomes a list of participants
        for cn in ['Informed', 'Naive']:
            evokeds[pt][cn] = list(); evokeds_dat[pt][cn] = list()
            # For every participant we average trials separately for all parts and conditions
            for vp in epochs.metadata['participant'].unique():
                query = 'participant == "' + vp + '" and part == "' + pt + '" and condition == "' + cn + '"'
                evokeds[pt][cn].append(epochs[query].average())
            # Compute grand averages across participants for this part and condition
            evokeds[pt][cn] = mne.grand_average(evokeds[pt][cn])
            # Export only the actual data for R
            evokeds_dat[pt][cn] = evokeds[pt][cn].data
    return (evokeds, evokeds_dat)

# Compute grand averages for Experiment 1
evokeds_exp1, evokeds_dat_exp1 = compute_evokeds(epochs=epochs_exp1)

import pickle
with open('analysis/export/exp1-avgs.pickle', 'wb') as handle:
    pickle.dump(evokeds_dat_exp1, handle, protocol=pickle.HIGHEST_PROTOCOL)
```

```{r backup}

test <- py$preproc(
  vhdr_fname = "data/exp1/EEG/Vp0001.vhdr",
  metadata = data_exp1[[1]],
  n_components = as.integer(15),
  method = "fastica",
  l_freq = 0.1,
  h_freq = 30,
  event_id = list(match = as.integer(221), mismatch = as.integer(222)),
  tmin = -0.5,
  tmax = 1.498,
  baseline = tuple(-0.2, 0),
  reject = list(eeg = 200))

test$ch_names
```

@@

```{r exp1-analysis}
# Re-import behavioral data and re-factorize some columns
data_exp1 <- py$epochs_exp1$metadata %>% mutate(
  part = factor(part, levels = c("I", "II", "III")),
  condition = factor(condition, levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")),
  participant = factor(participant),
  item = factor(item)
)

# Check number of rejected epochs
rejected_exp1 <- data_exp1 %>% group_by(participant) %>% tally() %>% mutate(n = 360 - n) %>% pull(n)
mean(rejected_exp1)    # Mean
median(rejected_exp1)  # Median
range(rejected_exp1)   # Range

# Create vectors with sample time points (in ms) and electrodes
times <- seq(py$preproc_params$tmin * 1000, py$preproc_params$tmax * 1000, 1 / py$epochs_exp1$info["sfreq"] * 1000)
els <- py$epochs_exp1$ch_names

# Define ERP components of interest
comps <- tibble(
  name = c("P1", "N170", "N400"),
  start = c(100, 150, 400),
  stop = c(150, 200, 700),
  roi = list(
    c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
    c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
    c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
  )
)

# Define function to compute single-trial mean ERP amplitudes
compute_erps <- function(epochs, els, name, start, stop, roi) {
  erps <- epochs[, which(els %in% roi), which(times %in% start:stop)]
  amps <- apply(erps, 1, mean, na.rm = TRUE)
  return(amps)
}

# # Define function to compute single-trial ERP latencies
# compute_lats <- function(epochs, els, name, start, stop, roi) {
#   erps <- epochs[, which(els %in% roi), which(times %in% start:stop)]
#   samples <- apply(erps, MARGIN = c(1, 3), mean) %>% abs()
#   areas <- apply(samples, MARGIN = 1, sum)
#   cumss <- apply(samples, MARGIN = 1, cumsum) %>% asplit(MARGIN = 2)
#   lats <- map2_int(cumss, areas, function(cums, area){which(cums < area / 2) %>% max()})
#   lats <- start + lats * 2
#   return(lats)
# }

# Check if single-trial ERPs were computed already (delete the file to re-run)
if (file.exists("analysis/export/exp1-erps.RDS")) {
  # Read data from file
  data_exp1 <- readRDS("analysis/export/exp1-erps.RDS")
} else {
  # Compute single-trial ERPs for Experiment 1
  data_exp1 <- pmap_dfc(comps, compute_erps, epochs = py$epochs_exp1$get_data(), els = els) %>%
    set_names(comps$name) %>%
    cbind(data_exp1, .) %T>%
    saveRDS("analysis/export/exp1-erps.RDS")
}

# Remove the epochs to free up memory
py_run_string("del epochs_exp1")
import("gc")$collect()

# Remove any trials excluded from conditions
data_exp1 %<>% filter(condition %in% c("Informed", "Naive")) %>% droplevels()

# Contrast coding for condition (informed-naive) and part (2-1, 3-1)
contrasts_condition <- t(cbind(c("Informed" = 1, "Naive" = -1)))
contrasts_part <- t(cbind(c("I" = -1, "II" = 1, "III" = 0), c("I" = 0, "II" = -1, "III" = 1)))
contrasts(data_exp1$condition) <- MASS::ginv(contrasts_condition)
contrasts(data_exp1$part) <- MASS::ginv(contrasts_part)

# Set formula and parameters for linear mixed-effects regression models (LMMs)
form_exp12 <- buildmer::tabulate.formula(
  ~ part * condition + (part * condition | participant) + (part * condition | item)
) %>% mutate(block = replace(block, is.na(grouping), "fixed"))
ctrl_params <- lme4::lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

# Set formula for follow-up contrasts
specs_exp12 <- pairwise ~ condition | part

# Define function to compute LMMs and follow-up contrasts for each component
compute_models <- function(dep, formula, data, control, specs) {
  require(lmerTest)
  require(buildmer)
  require(emmeans)
  build <- buildmer(
    control = control,
    REML = FALSE,
    buildmerControl = buildmerControl(
      formula = formula,
      data = data,
      direction = c("order", "backward"),
      elim = function(logp) exp(logp) >= .20,
      calc.anova = TRUE,
      ddf = "Satterthwaite",
      dep = dep
    )
  )
  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
  means <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$emmeans %>% as.data.frame()
  conts <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$contrasts %>% as.data.frame()
  mod <- list(model = build@model, anova = build@anova, summary = build@summary, means = means, contrasts = conts)
  return(mod)
}

# Check if models were computed already (delete the file to re-run)
if (file.exists("analysis/export/exp1-stats.RDS")) {
  # Read models from file
  models_exp1 <- readRDS("analysis/export/exp1-stats.RDS")
} else {
  # Compute LMMs for Experiment 1
  models_exp1 <- map(
    comps$name,
    compute_models,
    formula = form_exp12,
    data = data_exp1,
    control = ctrl_params,
    specs = specs_exp12
  ) %>% set_names(comps$name) %T>%
    saveRDS("analysis/export/exp1-stats.RDS")
}
```

@@

```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
# Locate standard montage file from MNE Python
fname_montage <- list.files(
  path = reticulate::py_discover_config()$python %>% str_remove("bin/.*"),
  pattern = "easycap-M1.txt", full.names = TRUE, recursive = TRUE
)[1]

# Retrieve locations for the relevant electrodes from this montage
montage <- py$evokeds_exp1$I$Informed$ch_names %>%
  as_tibble() %>%
  rename(electrode = value) %>%
  left_join(
    read_tsv(fname_montage, col_types = cols()) %>%
      rename(electrode = Site),
    by = "electrode"
  ) %>%
  mutate(
    x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
    y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi))
  )

@@

# Create plot for Experiment 1
plot_grid(
  plot_trials(),
  plot_erps(comps = comps, evokeds = py$evokeds_dat_exp1, models = models_exp1, montage = montage),
  nrow = 2, rel_heights = c(5, 6), labels = c("A", "B"), label_fontfamily = "Helvetica"
) + # Add some lines (to separate the parts) and the legend
  annotate(geom = "segment", x = 0.328, xend = 0.328, y = -Inf, yend = 0.53, linetype = "dashed") +
  annotate(geom = "segment", x = 0.672, xend = 0.672, y = -Inf, yend = 0.53, linetype = "dashed") +
  annotate(geom = "segment", x = 0.328, xend = 0.28, y = 0.53, yend = 0.58, linetype = "dashed") +
  annotate(geom = "segment", x = 0.672, xend = 0.72, y = 0.53, yend = 0.58, linetype = "dashed") +  
  annotate(geom = "segment", x = 0.28, xend = 0.28, y = 0.58, yend = Inf, linetype = "dashed") +
  annotate(geom = "segment", x = 0.72, xend = 0.72, y = 0.58, yend = Inf, linetype = "dashed") +
  draw_plot(plot_legends_erps(direction = "vertical"), x = 0.405, y = 0.422, width = 1, height = 1)
```

@@

First, because we were interested in the effects of knowledge on perceiving *unfamiliar* objects only, we excluded from all further analyses those objects which participants classified as being known to them in the pre-insight part (i.e., before any keywords were presented). This led to the exclusion of an average of `r format(round(stims_exp1["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(stims_exp1["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects). Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analyses was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \@ref(fig:exp1-plot)A). Objects were assigned to the semantically informed condition only if they were presented with matching keywords *and* if participants indicated knowing what the object was or having an assumption. This was the case for an average of `r format(round(stims_exp1["Informed"], 1), nsmall = 1)` objects per participant (= `r scales::percent(stims_exp1["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords). Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords *and* if participants indicated not knowing what the object was or having rather no assumption. This was the case for an average of `r format(round(stims_exp1["Naive"], 1), nsmall = 1)` objects per participant (= `r scales::percent(stims_exp1["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords). Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occur---the same assignment was used to analyze the data from the other two parts. This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any lasting effects on a subsequent, third presentation of the objects (post-insight part).

@@

# Check average number of stimuli per condition
(stims_exp2 <- map(data_exp2, function(x) {table(x$condition) / 3}) %>% bind_rows() %>% colMeans())
```

@@

All materials, procedures, EEG-related methods, and statistical analyses were identical to Experiment 1. An average of `r format(round(stims_exp2["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(stims_exp2["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects) was classified as being known in the pre-insight part and excluded from all further analyses. Based on participants' responses in the insight part, an average of `r format(round(stims_exp2["Informed"], 1), nsmall = 1)` objects were assigned to the semantically informed condition (= `r scales::percent(stims_exp2["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords) and an average of `r format(round(stims_exp2["Naive"], 1), nsmall = 1)` objects were assigned to the naive condition (= `r scales::percent(stims_exp2["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords). Automatic rejection of EEG epochs containing artifacts led to the exclusion of `r format(round(mean(rejected_exp2), 1), nsmall = 1)` trials per participant (= `r scales::percent(mean(rejected_exp2)/360, accuracy = 0.1)`; range `r min(rejected_exp2)` to `r max(rejected_exp2)` trials).

>>>>

```{r setup, include=FALSE}
# Do you want to re-run the EEG preprocessing? Note that this can only be done with the raw data,
# which are available from the corresponding author (rasha.abdel.rahman@hu-berlin.de) upon request.
rerun_preproc <- FALSE

# Do you want to re-run the linear mixed-effect models? This can be done even if only the
# preprocessed single-trial data are available (from GitHub and/or the OSF). Note, however, that
# fitting all models may take 24 hours or more.
rerun_models <- FALSE

# Load packages
library(papaja)
library(reticulate)
library(tidyverse)
library(magrittr)
library(cowplot)

@@

# Define ERP components of interest
comps <- tibble(
  name = c("P1", "N170", "N400"),
  start = c(100, 150, 400),
  stop = c(150, 200, 700),
  roi = list(
    c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
    c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
    c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
  )
)
```

@@

```{python def_functions, eval=rerun_preproc}
# Import libraries
import mne

@@

# # Define function to compute grand averages per condition
# def compute_evokeds(epochs):
#     evokeds = dict(); evokeds_dat = dict()
#     # Each part becomes a dictionary of conditions
#     for pt in ['I', 'II', 'III']:
#         evokeds[pt] = dict(); evokeds_dat[pt] = dict()
#         # Each condition becomes a list of participants
#         for cn in ['Informed', 'Naive']:
#             evokeds[pt][cn] = list(); evokeds_dat[pt][cn] = list()
#             # For every participant we average trials separately for all parts and conditions
#             for vp in epochs.metadata['participant'].unique():
#                 query = 'participant == "' + vp + '" and part == "' + pt + '" and condition == "' + cn + '"'
#                 evokeds[pt][cn].append(epochs[query].average())
#             # Compute grand averages across participants for this part and condition
#             evokeds[pt][cn] = mne.grand_average(evokeds[pt][cn])
#             # Export only the actual data for R
#             evokeds_dat[pt][cn] = evokeds[pt][cn].data
#     return (evokeds, evokeds_dat)

# Define function to compute averaged waveforms by part and condition
def compute_evokeds(epochs, grand=True, data_only=True):
  # Define lists of participants, parts, and conditions
  ps = epochs.metadata['participant'].unique()
  pts = ['I', 'II', 'III']
  cns = ['Informed', 'Naive']
  # Define function to compute a single by-participant waveform
  def compute_evoked(epochs, pt, cn, p):
    query = 'participant == "' + p + '" and part == "' + pt + '" and condition == "' + cn + '"'
    return(epochs[query].average())
  # Create a dict with by-participant waveforms nested in conditions nested in parts
  avgs = {pt:{cn:[compute_evoked(epochs, pt, cn, p) for p in ps] for cn in cns} for pt in pts}
  # If needed, compute grand-averaged waveforms across participants
  if grand:
    avgs = {pt:{cn:mne.grand_average(avgs[pt][cn]) for cn in cns} for pt in pts}
  # If needed, extract only the data from the evoked MNE objects
  if data_only:
    if grand:
      avgs = {pt:{cn:avgs[pt][cn].data for cn in cns} for pt in pts}
    else:
      avgs = {pt:{cn:[avgs[pt][cn][p].data for p in range(0, len(ps))] for cn in cns} for pt in pts}
  return(avgs)

```

```{r exp1-preproc, eval=rerun_preproc}
# Define function for reading and formatting the behavioral data
read_behav <- function(txt_fname) {
  # Read the log file
  dat <- suppressWarnings(read_tsv(txt_fname, col_types = cols()))
  # Rename columns for participant and item IDs
  dat %<>% rename(participant = VPNummer, item = StimID) %>%
    # Add a column for the part of the experiment
    mutate(part = case_when(
      Wdh %in% c(211, 231) ~ "I",
      Wdh %in% c(212, 232) ~ "II",
      Wdh %in% c(213, 233) ~ "III",
      Wdh == 234 ~ "IV"
    ) %>% as_factor()) %>%
    # Remove filler stimuli (i.e.,well-known objects)
    filter(bek_unbek != "bekannt")
  # Assign stimuli to conditions based on keywords and button presses
  excl_known <- dat %>%
    filter(part == "I" & Tastencode %in% c(201, 251)) %>%
    pull(item)
  excl_informed <- dat %>%
    filter(part == "II" & grepl("richtig", Bed) & !Tastencode %in% c(201, 202, 251, 252)) %>%
    pull(item)
  excl_naive <- dat %>%
    filter(part == "II" & grepl("falsch", Bed) & !Tastencode %in% c(203, 204, 253, 254)) %>%
    pull(item)
  informed <- dat %>%
    filter(part == "II" & grepl("richtig", Bed) & Tastencode %in% c(201, 202, 251, 252)) %>%
    pull(item)
  naive <- dat %>%
    filter(part == "II" & grepl("falsch", Bed) & Tastencode %in% c(203, 204, 253, 254)) %>%
    pull(item)
  # Create a new condition for the experimental condition
  dat %<>% mutate(condition = case_when(
    item %in% excl_known ~ "Excl_known",
    item %in% excl_informed ~ "Excl_informed",
    item %in% excl_naive ~ "Excl_naive",
    item %in% informed ~ "Informed",
    item %in% naive ~ "Naive"
  ) %>% factor(levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")))
  # In Experiment 3, we need an additional column for position (upright vs. inverted)
  if ("richtig_inv" %in% dat$Bed) {
    dat %<>% mutate(position = as_factor(ifelse(grepl("inv", Bed), "Inverted", "Upright"))) %>%
      # Return only relevant columns
      select(part, position, condition, participant, item, RT)
  } else {
    # Return only relevant columns
    dat %<>% select(part, condition, participant, item, RT)
  }
  return(dat)
}

# Read behavioral data for Experiment 1
list.files("data/exp1/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav) -> behav_exp1

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp1, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp1$participant), .before = 1) %>%
  #summarise(across(.fns = mean)) %>%
  #pivot_longer(cols = everything(), names_to = "condition", values_to = "objects") %T>%
  write_tsv("analysis/export/exp1-objects.tsv")

# Define global parameters for EEG preprocessing
preproc_params <- list(
  # Number of ICA components
  n_components = as.integer(15),
  # ICA methods
  method = "fastica",
  # Lower edge of pass-band filter
  l_freq = 0.1,
  # Upper edge of pass-band filter
  h_freq = 30,
  # Event trigger codes
  event_id = dict(match = 221, mismatch = 222),
  # Beginning of epochs in s
  tmin = -0.5,
  # End of epochs in s
  tmax = 1.498,
  # Baseline interval in s
  baseline = tuple(-0.2, 0),
  # Artifact rejection threshold in microvolts
  reject = dict(eeg = 200)
)

# Actually apply the preprocessing function for Epxeriment 1 in Python
map2(
  .x = list.files("data/exp1/EEG", pattern = ".vhdr", full.names = TRUE),
  .y = behav_exp1,
  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
) %>%
  # Concatenate epochs of all participants
  py$mne$epochs$concatenate_epochs() -> epochs_exp1

# Backup epochs to the export folder
epochs_exp1$save("analysis/export/exp1-epo.fif")

# Get standard EasyCap electrode positions and project to 2D space
py$mne$channels$`_standard_montage_utils`$MONTAGE_PATH %>%
  list.files(pattern = "easycap-M1.txt", full.names = TRUE) %>%
  read_tsv(col_types = cols()) %>%
  rename(electrode = Site) %>%
  inner_join(tibble(electrode = epochs_exp1$ch_names), ., by = "electrode") %>%
  mutate(
    x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
    y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
  ) %>%
  write_tsv("analysis/export/montage.tsv")

# Create a vector with sample time points (in ms)
sfreq <- epochs_exp1$info["sfreq"]
seq(preproc_params$tmin * 1000, preproc_params$tmax * 1000, 1 / sfreq * 1000) %T>%
  cat(file = "analysis/export/sample_times.tsv", sep = "\n") -> times

# Define function to compute single-trial mean ERP amplitudes
compute_erps <- function(epochs, name, start, stop, roi) {
  dat <- epochs$get_data()
  els <- epochs$ch_names
  erps <- dat[, which(els %in% roi), which(times %in% start:stop)]
  amps <- apply(erps, 1, mean, na.rm = TRUE)
  return(amps)
}

# Actually apply the function to compute mean ERP amplitudes for Experiment 1
pmap_dfc(comps, compute_erps, epochs = epochs_exp1) %>%
  set_names(comps$name) %>%
  # Bind to the behavioral data
  bind_cols(as_tibble(epochs_exp1$metadata), .) %T>%
  # Backup to the export folder
  write_tsv("analysis/export/exp1-erps.tsv") -> data_exp1

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp1, grand = TRUE, data_only = TRUE) %>%
  saveRDS("analysis/export/exp1-gavgs.RDS")
```

@@

```{r exp1-models, eval=rerun_models}
# Load preprocessed single-trial data
read_tsv("analysis/export/exp1-erps.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) %>%
  # Remove any trials excluded from conditions
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> data_exp1

# Define contrast coding for condition (informed-naive) and part (2-1, 3-1)
contrasts_condition <- t(cbind(
  c("Informed" = 1, "Naive" = -1)
))
contrasts_part <- t(cbind(
  c("I" = -1, "II" = 1, "III" = 0),
  c("I" = 0, "II" = -1, "III" = 1)
))

# Apply these contrasts to the factors in the data
contrasts(data_exp1$condition) <- MASS::ginv(contrasts_condition)
contrasts(data_exp1$part) <- MASS::ginv(contrasts_part)

# Define formula and parameters for linear mixed-effects regression models (LMMs)
formula_exp12 <- buildmer::tabulate.formula(
  ~ part * condition + (part * condition | participant) + (part * condition | item)
) %>% mutate(block = replace(block, is.na(grouping), "fixed"))
control <- lme4::lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

# Define formula for follow-up contrasts
specs_exp12 <- pairwise ~ condition | part

# Define function to compute LMMs and follow-up contrasts for each component
compute_models <- function(dep, formula, data, control, specs) {
  require(lmerTest)
  require(buildmer)
  require(emmeans)
  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
  build <- buildmer(
    control = control,
    REML = FALSE,
    buildmerControl = buildmerControl(
      formula = formula,
      data = data,
      direction = c("order", "backward"),
      elim = function(logp) exp(logp) >= .20,
      calc.anova = TRUE,
      ddf = "Satterthwaite",
      dep = dep
    )
  )
  means <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$emmeans
  conts <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$contrasts
  modlist <- list(
    model = build@model,
    anova = build@anova,
    summary = build@summary,
    means = means %>% as.data.frame(),
    contrasts = conts %>% as.data.frame()
  )
  return(modlist)
}

# Actually apply the function to compute the models for Experiment 1
map(
  comps$name,
  compute_models,
  formula = formula_exp12,
  data = data_exp1,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/exp1-mods.RDS") -> models_exp1
```

@@

```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
# # For debugging
# epochs_exp1 <- py$mne$read_epochs("analysis/export/exp1-epo.fif")

# Compute average number of objects per condition
(read_tsv("analysis/export/exp1-objects.tsv", col_types = cols()) %>%
   summarise(across(.cols = -Participant, .fns = mean)) %>%
   slice(1) %>% unlist() -> objects_exp1)

# Load preprocessed single-trial data
read_tsv("analysis/export/exp1-erps.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) -> data_exp1

# Check number of rejected epochs
data_exp1 %>%
  group_by(participant) %>%
  tally() %>%
  mutate(n = 360 - n) %>%
  pull(n) -> rejected_exp1
mean(rejected_exp1)    # Mean
median(rejected_exp1)  # Median
range(rejected_exp1)   # Range

# Load sample time points and electrode montage
times <- scan("analysis/export/sample_times.tsv", quiet = TRUE)
montage <- read_tsv("analysis/export/montage.tsv", col_types = cols())

# Load grand-averaged ERPs and linear mixed models
evokeds_exp1 <- readRDS("analysis/export/exp1-gavgs.RDS")
models_exp1 <- readRDS("analysis/export/exp1-mods.RDS")

@@

# Create plot for Experiment 1
plot_grid(
  plot_trials(),
  plot_erps(comps = comps, evokeds = evokeds_exp1, models = models_exp1, montage = montage),
  nrow = 2, rel_heights = c(5, 6), labels = c("A", "B"), label_fontfamily = "Helvetica"
) + # Add some lines (to separate the parts) and the legend
  annotate(geom = "segment", x = 0.328, xend = 0.328, y = -Inf, yend = 0.53, linetype = "dashed") +
  annotate(geom = "segment", x = 0.672, xend = 0.672, y = -Inf, yend = 0.53, linetype = "dashed") +
  annotate(geom = "segment", x = 0.328, xend = 0.28, y = 0.53, yend = 0.58, linetype = "dashed") +
  annotate(geom = "segment", x = 0.672, xend = 0.72, y = 0.53, yend = 0.58, linetype = "dashed") +  
  annotate(geom = "segment", x = 0.28, xend = 0.28, y = 0.58, yend = Inf, linetype = "dashed") +
  annotate(geom = "segment", x = 0.72, xend = 0.72, y = 0.58, yend = Inf, linetype = "dashed") +
  draw_plot(plot_legends_erps(direction = "vertical"), x = 0.405, y = 0.422, width = 1, height = 1)
```

@@

First, because we were interested in the effects of knowledge on perceiving *unfamiliar* objects only, we excluded from all further analyses those objects which participants classified as being known to them in the pre-insight part (i.e., before any keywords were presented). This led to the exclusion of an average of `r format(round(objects_exp1["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp1["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects). Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analyses was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \@ref(fig:exp1-plot)A). Objects were assigned to the semantically informed condition only if they were presented with matching keywords *and* if participants indicated knowing what the object was or having an assumption. This was the case for an average of `r format(round(objects_exp1["Informed"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp1["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords). Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords *and* if participants indicated not knowing what the object was or having rather no assumption. This was the case for an average of `r format(round(objects_exp1["Naive"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp1["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords). Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occur---the same assignment was used to analyze the data from the other two parts. This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any lasting effects on a subsequent, third presentation of the objects (post-insight part).

@@

# Check average number of stimuli per condition
(objects_exp2 <- map(data_exp2, function(x) {table(x$condition) / 3}) %>% bind_rows() %>% colMeans())
```

@@

All materials, procedures, EEG-related methods, and statistical analyses were identical to Experiment 1. An average of `r format(round(objects_exp2["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp2["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects) was classified as being known in the pre-insight part and excluded from all further analyses. Based on participants' responses in the insight part, an average of `r format(round(objects_exp2["Informed"], 1), nsmall = 1)` objects were assigned to the semantically informed condition (= `r scales::percent(objects_exp2["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords) and an average of `r format(round(objects_exp2["Naive"], 1), nsmall = 1)` objects were assigned to the naive condition (= `r scales::percent(objects_exp2["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords). Automatic rejection of EEG epochs containing artifacts led to the exclusion of `r format(round(mean(rejected_exp2), 1), nsmall = 1)` trials per participant (= `r scales::percent(mean(rejected_exp2)/360, accuracy = 0.1)`; range `r min(rejected_exp2)` to `r max(rejected_exp2)` trials).
